---
output: html_document
---

This document provides a detailed explanation of the data processing and analysis steps involved in normalizing identifiers, transforming data, imputing missing values, and calculating weights and adjustments. Each section contains R code snippets along with comprehensive explanations to help in understanding the process.


# 1. Normalize Identifiers

In this step, we extract `school_ID` and `class_ID` from the column names of the `raw_data` dataframe. These identifiers are essential for subsequent data processing steps. We also rename these columns to lowercase for consistency.

```{r, eval = FALSE, echo = TRUE}
# Extract school and class identifiers from column names
school_id_col <- grep("school_ID", colnames(raw_data), value = TRUE)
class_id_col <- grep("class_ID", colnames(raw_data), value = TRUE)

# Rename columns to lowercase
colnames(raw_data)[colnames(raw_data) == school_id_col] <- "school_id"
colnames(raw_data)[colnames(raw_data) == class_id_col] <- "class_id"
```

**Explanation:**
  - `grep("school_ID", colnames(raw_data), value = TRUE)` searches for the column name that contains "school_ID" and returns its name.
- We then use `colnames(raw_data)[colnames(raw_data) == school_id_col] <- "school_id"` to rename the column to "school_id".
- The same process is repeated for `class_ID`.

# 2. Transform Sex and Grade Data

In this section, we copy the `DE_SEX` and `DE_GRADE` columns to new columns (`SAMPL_SEX`, `char_SAMPL_SEX`, `SAMPL_GRADE`, and `char_SAMPL_GRADE`). These new columns will be used for further data transformations. We also convert these columns to factors to facilitate categorical data analysis.

```{r, eval = FALSE, echo = TRUE}
# Copy and factorize sex and grade columns
raw_data$SAMPL_SEX <- raw_data$DE_SEX
raw_data$char_SAMPL_SEX <- raw_data$DE_SEX
raw_data$SAMPL_GRADE <- raw_data$DE_GRADE
raw_data$char_SAMPL_GRADE <- raw_data$DE_GRADE

# Convert sex and grade columns to factors
raw_data$SAMPL_SEX <- as.factor(raw_data$SAMPL_SEX)
raw_data$SAMPL_GRADE <- as.factor(raw_data$SAMPL_GRADE)
```

**Explanation:**
- We copy the values of `DE_SEX` and `DE_GRADE` to new columns for further processing.
- `as.factor()` converts the columns to factors, which is useful for categorical data operations.

# 3. Impute Missing Data

Missing data can bias the analysis, so we impute missing values for sex and grade based on the proportions within each school.

## Impute Missing Sex Data

We calculate the proportion of each sex within each school and use these proportions to probabilistically impute missing sex values.

```{r, eval = FALSE, echo = TRUE}
# Calculate sex proportions within each school
sex_school_lookup <- raw_data %>%
  group_by(school_id) %>%
  count(DE_SEX) %>%
  mutate(prop = n / sum(n)) %>%
  select(-n) %>%
  spread(DE_SEX, prop, fill = 0)

# Impute missing sex values
raw_data <- raw_data %>%
  rowwise() %>%
  mutate(char_SAMPL_SEX = ifelse(is.na(char_SAMPL_SEX),
                                 sample(c("F", "M"), 1, prob = c(sex_school_lookup$F[school_id == school_id], sex_school_lookup$M[school_id == school_id])),
                                 char_SAMPL_SEX))
```

**Explanation:**
  - We calculate the proportion of each sex (`F` and `M`) within each school using `group_by(school_id)` and `count(DE_SEX)`.
- The `mutate()` function creates a new column `prop` that represents the proportion of each sex within the school.
- `spread(DE_SEX, prop, fill = 0)` reshapes the data so that each sex has its own column with the corresponding proportion.
- The `ifelse()` function in `mutate()` imputes missing sex values by sampling from `F` and `M` based on the calculated proportions.

## Impute Missing Grade Data

Similarly, we calculate the proportions of each grade within each school and class, and use these proportions to impute missing grade values.

```{r, eval = FALSE, echo = TRUE}
# Calculate grade proportions within each school and class
grade_school_lookup <- raw_data %>%
  group_by(school_id, class_id) %>%
  count(DE_GRADE) %>%
  mutate(prop = n / sum(n)) %>%
  select(-n) %>%
  spread(DE_GRADE, prop, fill = 0)

# Impute missing grade values
raw_data <- raw_data %>%
  rowwise() %>%
  mutate(char_SAMPL_GRADE = ifelse(is.na(char_SAMPL_GRADE),
                                   sample(names(grade_school_lookup)[-c(1, 2)], 1, prob = grade_school_lookup[school_id == school_id & class_id == class_id, -c(1, 2)]),
                                   char_SAMPL_GRADE))
```

**Explanation:**
  - We calculate the proportion of each grade within each school and class using `group_by(school_id, class_id)` and `count(DE_GRADE)`.
- The `mutate()` function creates a new column `prop` that represents the proportion of each grade within the school and class.
- `spread(DE_GRADE, prop, fill = 0)` reshapes the data so that each grade has its own column with the corresponding proportion.
- The `ifelse()` function in `mutate()` imputes missing grade values by sampling from the grades based on the calculated proportions.

# 4. Load and Process External Data

We load the `frame_schools` and `sample_schools` data from Excel files. These datasets provide additional information about schools, which is necessary for further analysis. We also normalize the column names to lowercase for consistency.

```{r, eval = FALSE, echo = TRUE}
# Load Excel files
frame_schools <- read_excel("Frame_Schools.xlsx")
sample_schools <- read_excel("Sample_Schools.xlsx")

# Normalize column names
colnames(frame_schools) <- tolower(colnames(frame_schools))
colnames(sample_schools) <- tolower(colnames(sample_schools))
```

**Explanation:**
  - `read_excel("Frame_Schools.xlsx")` and `read_excel("Sample_Schools.xlsx")` load the data from Excel files into dataframes.
- We use `tolower(colnames())` to convert all column names to lowercase to maintain consistency.

## Calculate Enrollments

We calculate the total enrollments for each school by summing the female and male enrollments. Additionally, we categorize schools into quantile groups based on their total enrollments for further analysis.

```{r, eval = FALSE, echo = TRUE}
# Add total enrollments for each school
frame_schools$total_enrollment <- frame_schools$enrollment_female + frame_schools$enrollment_male
sample_schools$total_enrollment <- sample_schools$enrollment_female + sample_schools$enrollment_male

# Categorize schools into quantile groups based on enrollment
sample_schools$enrollment_quantile <- cut(sample_schools$total_enrollment, breaks = quantile(sample_schools$total_enrollment, probs = seq(0, 1, by = 0.2)), include.lowest = TRUE, labels = FALSE)
```

**Explanation:**
  - We calculate the total enrollment by summing `enrollment_female` and `enrollment_male` for each school.
- `cut()` function categorizes schools into quantile groups based on their total enrollments. This helps in stratifying schools for further analysis.

# 5. Compute Weights and Adjustments

## School Non-Response Adjustment

To adjust for non-response, we calculate non-response adjustment factors and adjust the school weights accordingly.

```{r, eval = FALSE, echo = TRUE}
# Compute non-response adjustment factor
non_response_adjustment <- sample_schools %>%
  group_by(enrollment_quantile) %>%
  summarize(non_response_adjustment = n() / n_distinct(frame_schools$school_id[frame_schools$enrollment_quantile == enrollment_quantile]))

# Adjust school weights
sample_schools <- sample_schools %>%
  left_join(non_response_adjustment, by = "enrollment_quantile") %>%
  mutate(adjusted_school_weight = school_weight * non_response_adjustment)
```

**Explanation:**
  - We calculate the non-response adjustment factor by dividing the number of responding schools by the total number of schools within each enrollment quantile.
- `left_join(non_response_adjustment, by = "enrollment_quantile")` merges the adjustment factor with the `sample_schools` dataframe.
- The `mutate()` function adjusts the school weights using the non-response adjustment factor.

## Transform School Sample to Long Format

We reshape the school sample data from wide to long format for easier manipulation and analysis.

```{r, eval = FALSE, echo = TRUE}
# Reshape school sample data to long format
school_sample_long <- sample_schools %>%
  gather(key = "class_id", value = "class_value", -school_id, -adjusted_school_weight)
```

**Explanation

:**
  - The `gather()` function reshapes the data from wide to long format, where each row represents a unique combination of `school_id`, `class_id`, and `class_value`.

## Class Participation and Student Weights

We calculate the number of classes that participated per school and compute pre-stratification weights for students.

```{r, eval = FALSE, echo = TRUE}
# Calculate number of classes participated per school
school_sample_long <- school_sample_long %>%
  group_by(school_id) %>%
  mutate(classes_participated = n_distinct(class_id))

# Compute pre-stratification weights for students
school_sample_long <- school_sample_long %>%
  mutate(pre_strat_weight = adjusted_school_weight / classes_participated)
```

**Explanation:**
  - We calculate the number of classes that participated per school using `n_distinct(class_id)`.
- `mutate(pre_strat_weight = adjusted_school_weight / classes_participated)` computes the pre-stratification weight for each student by dividing the adjusted school weight by the number of classes that participated.

## Categorize Sample Schools

We assign numerical categories to schools based on their original categories for further stratification and primary sampling unit (PSU) assignment.

```{r, eval = FALSE, echo = TRUE}
# Assign numerical categories to schools
school_sample_long <- school_sample_long %>%
  mutate(school_category = as.numeric(factor(school_category)))
```

**Explanation:**
  - The `factor()` function converts categorical variables to factors, and `as.numeric()` assigns numerical values to these factors, which facilitates further stratification.

# 6. Stratification and PSU Assignment

## Assign Strata and PSUs

We split the sample into two sets based on whether the school weight was trimmed, assign strata by pairing schools within each category, and assign primary sampling units (PSUs) based on these strata.

```{r, eval = FALSE, echo = TRUE}
# Split the sample into two sets based on trimmed school weight
non_trimmed_weights <- school_sample_long %>% filter(adjusted_school_weight != 1)
trimmed_weights <- school_sample_long %>% filter(adjusted_school_weight == 1)

# Assign strata by pairing schools within each category
non_trimmed_weights <- non_trimmed_weights %>%
  group_by(school_category) %>%
  mutate(strata = (row_number() - 1) %/% 2 + 1)

# Assign PSUs based on strata
non_trimmed_weights <- non_trimmed_weights %>%
  mutate(psu = strata)

# Assign strata individually for trimmed weights
trimmed_weights <- trimmed_weights %>%
  mutate(strata = row_number() + max(non_trimmed_weights$strata))

# Combine the two sets
combined_weights <- bind_rows(non_trimmed_weights, trimmed_weights)
```

**Explanation:**
  - We split the sample into two sets: `non_trimmed_weights` and `trimmed_weights` based on whether the school weight was trimmed.
- `mutate(strata = (row_number() - 1) %/% 2 + 1)` assigns strata by pairing schools within each category.
- `mutate(psu = strata)` assigns primary sampling units (PSUs) based on these strata.
- For trimmed weights, we assign strata individually and ensure they do not overlap with the strata of non-trimmed weights.
- Finally, we combine the two sets using `bind_rows()`.

