---
output: html_document
---

## Calculate Degrees of Freedom

```{r, eval = FALSE, echo = TRUE}
# Calculate degrees of freedom for survey design
degrees_freedom <- degf(svy_data3) - 1
```

**Explanation:**
- `degf(svy_data3)` calculates the degrees of freedom for the survey design `svy_data3`. Subtracting 1 (`- 1`) adjusts for the estimation of population parameters from sample data.

## Function: summary_table_fn

```{r, eval = FALSE, echo = TRUE}
# Function to generate summary tables for a specified variable
summary_table_fn <- function(variable = 'DB_B_HUNGRY') {
  
  # Get the number variable from language titles
  num_var <- eval(parse(text = lang_titles[1]))[1]
  
  # Construct formula based on variable and number condition
  eval(parse(text = paste0('formula = ~I(', variable, '=="', num_var, '")')))
  
  # Define condition to filter non-missing values
  cond1 <- paste0('!is.na(', variable, ')')
  
  # Function to estimate confidence interval proportion
  ciprop_function <- function(cond_subset = 'DE_SEX==""') {
    # Number of participants and estimated CI
    if (cond_subset != '') {
      n_participants <- data %>%
        filter(eval(parse(text = paste0(cond_subset, '&', cond1)))) %>%
        summarise(n()) %>%
        as.numeric()
      
      if (n_participants >= n_cutoff) {
        est_ciprop <- svyciprop(formula, design = subset(svy_data3, eval(parse(text = cond_subset))), method = "lo", df = degrees_freedom)
      } else {
        est_ciprop <- '-'
      }
    } else {
      n_participants <- data %>%
        filter(eval(parse(text = cond1))) %>%
        summarise(n()) %>%
        as.numeric()
      
      if (n_participants >= n_cutoff) {
        est_ciprop <- svyciprop(formula, design = subset(svy_data3, eval(parse(text = cond1))), method = "lo", df = degrees_freedom)
      } else {
        est_ciprop <- '-'
      }
    }
    
    # Format proportion and confidence interval
    total_est <- ifelse(n_participants >= n_cutoff, formatC(round(as.vector(est_ciprop) * 100, 1), format = 'f', digits = 1), '-')
    est_ci <- ifelse(n_participants >= n_cutoff, paste0('(', formatC(round((as.numeric(attr(est_ciprop, "ci")[1])) * 100, 1), format = 'f', digits = 1), ' - ', formatC(round(100 * as.numeric(attr(est_ciprop, "ci")[2]), 1), format = 'f', digits = 1), ')'), '-')
    
    # Combine results into a data frame
    result <- bind_cols(total_est, est_ci, n_participants) %>% data.frame()
    colnames(result) <- c('Percent', 'CI', 'N')
    
    return(result)
  }
  
  ### Call ciprop_function for different subsets
  
  # Define age and sex category levels
  age_cat_levels <- paste0("age_cat == '", levels(data$age_cat), "'")
  sex_cat_levels <- paste0("DE_SEX == '", levels(data$DE_SEX), "'")  # Sex
  
  # Define class/grade category levels
  class_cat_levels <- paste0("DE_GRADE == '", levels(data$DE_GRADE), "'")  # Class/grade
  
  # Define male and female age category levels
  male_age_cat_levels <- paste0("DE_SEX == '", levels(data$DE_SEX)[1], "' & ", "age_cat == '", levels(data$age_cat), "'")
  female_age_cat_levels <- paste0("DE_SEX == '", levels(data$DE_SEX)[2], "' & ", "age_cat == '", levels(data$age_cat), "'")
  
  # Define male and female class/grade category levels
  male_class_cat_levels <- paste0("DE_SEX == '", levels(data$DE_SEX)[1], "' & ", "DE_GRADE == '", levels(data$DE_GRADE), "'")
  female_class_cat_levels <- paste0("DE_SEX == '", levels(data$DE_SEX)[2], "' & ", "DE_GRADE == '", levels(data$DE_GRADE), "'")
  
  # Define class level conditions
  class_conditions <- NULL
  for (k in 1:length(levels(data$DE_GRADE))) {
    class_level_cond <- c(class_cat_levels[k], male_class_cat_levels[k], female_class_cat_levels[k])
    class_conditions <- c(class_conditions, class_level_cond)
  }
  
  # Define all conditions
  all_conditions <- c('', sex_cat_levels,
                     age_cat_levels[1], male_age_cat_levels[1], female_age_cat_levels[1],
                     age_cat_levels[2], male_age_cat_levels[2], female_age_cat_levels[2],
                     age_cat_levels[3], male_age_cat_levels[3], female_age_cat_levels[3],
                     '(age_cat == "13 - 15" | age_cat == "16 or 17")', paste0('DE_SEX == "', levels(data$DE_SEX)[1], '" & (age_cat == "13 - 15" | age_cat == "16 or 17")'),
                     paste0('DE_SEX == "', levels(data$DE_SEX)[2], '" & (age_cat == "13 - 15" | age_cat == "16 or 17")'),
                     age_cat_levels[4], male_age_cat_levels[4], female_age_cat_levels[4],
                     class_conditions)
  
  # Apply ciprop_function in parallel
  list_point_plus_ci_est <- parallel::mclapply(all_conditions, ciprop_function, mc.cores = num_cores, mc.preschedule = FALSE)
  
  # Combine all results into a matrix
  all_point_plus_ci_est <- do.call('cbind', list_point_plus_ci_est)
  
  # Determine lower limits for each section in the output table
  lower_limits <- c()
  for (x in 1:length(all_point_plus_ci_est)) {
    if (x %% 9 == 0 & (x > 45 & x < length(all_point_plus_ci_est))) {
      lower_limits <- c(lower_limits, x + 1)
    } else {
      NULL
    }
  }
  
  # Create class table with labels
  eval(parse(text = paste0('class_tab = rbind(', paste0('c("', levels(data$DE_GRADE), '", all_point_plus_ci_est[', lower_limits, ':', lower_limits + 8, '])', collapse = ','), ')')))
  
  # Get text outputs from language titles
  text_output <- eval(parse(text = lang_titles[18]))
  
  # Construct output table
  output_table <- rbind(c(text_output[1], all_point_plus_ci_est[1:9]),
                        c(text_output[2], rep('', 9)),
                        c(text_output[3], all_point_plus_ci_est[10:18]),
                        c(text_output[4], all_point_plus_ci_est[19:27]),
                        c(text_output[5], all_point_plus_ci_est[28:36]),
                        c(text_output[6], all_point_plus_ci_est[37:45]),
                        c(text_output[7], all_point_plus_ci_est[46:54]),
                        c(text_output[8], rep('', 9)),
                        class_tab)
  
  # Prepare for flextable creation
  tab_names <- colnames(output_table)
  table_title <- paste0(variable, ': ', label(eval(parse(text = paste0('data$', variable)))))

  # Create formatted flextable object
  table_output <- output_table %>%
    as.data.frame() %>%
    mutate(across(everything(), as.character))  # Ensure all columns are character
  
  # Handle language-specific formatting
  if (language == 'FRENCH') {
    table_output <- eval(parse(text = paste0('cbind(', paste0(gsub('\\.', ',', table_output), collapse = ','), ')'))) %>%
      as.data.frame()
  } else {
    NULL
  }
  
  # Generate and format flextable
  table_output <- table_output %>%
    flextable() %>%
    autofit() %>%
    delete_part(part = "header") %>%
    add_header_lines(table_title) %>%
    flextable::style(pr_t = fp_text(font.family = 'Source Sans Pro'), part = 'all') %>%
    bold(i = c(1:2, 4, 10)) %>%
    bg(bg = "white", i = 1, part = "header") %>%
    hline_top(border = fp_border_default(width = 0), part = "header") %>%
    vline_left(i = 1, border = fp_border_default(width = 0), part = "header") %>%
    vline(i = 

1, border = fp_border_default(width = 0), part = "header") %>%
    align(align = "center", j = 2:10, part = "all") %>%
    width(j = 1:10, 3, unit = "in") %>%
    fontsize(size = 9, part = "all")
  
  return(table_output)
}
```

**Explanation:**
- The `summary_table_fn` function calculates the proportion and confidence interval for a specified variable across various demographic conditions (`age`, `sex`, `class`). It utilizes parallel processing (`mclapply`) for efficiency.
- **Degrees of Freedom Calculation:** `degrees_of_freedom <- degf(svy_data3) - 1` adjusts degrees of freedom for survey weights.
  
## Generate Summary Tables

```{r, eval = FALSE, echo = TRUE}
# Generate summary tables for all new variables in parallel
all_summary_tables <- parallel::mclapply(new_variables, summary_table_fn, mc.cores = num_cores, mc.preschedule = FALSE)

# Combine each summary table into separate Word documents
for (i in 1:length(new_variables)) {
  my_doc <- read_docx(paste0(getwd(), '/templates/Table_summary_template.docx'))
  summary_tables <- all_summary_tables[[i]]
  
  if (i < length(new_variables)) {
    my_doc <- my_doc %>%
      body_add_flextable(width(summary_tables, width = dim(summary_tables)$widths * 10 / (flextable_dim(summary_tables)$widths)), pos = 'on') %>%
      body_add_break()   
  } else {
    my_doc <- my_doc %>%
      body_add_flextable(width(summary_tables, width = dim(summary_tables)$widths * 10 / (flextable_dim(summary_tables)$widths)), pos = 'on') 
  }
  
  # Print each summary table document
  print(my_doc, target = paste0(getwd(), '/temp_tables/tempsum', i, '.docx')) 
}

# Combine all generated summary tables into a single document
combined_sum_doc <- read_docx(paste0(getwd(), '/templates/Table_summary_template.docx'))
combined_sum_doc <- headers_replace_text_at_bkm(combined_sum_doc, "country", site_name)
combined_sum_doc <- headers_replace_text_at_bkm(combined_sum_doc, "year", paste0(lang_titles[21], ' ', survey_year))
combined_sum_doc <- headers_replace_text_at_bkm(combined_sum_doc, "Summary", lang_titles[25])
combined_sum_doc <- footers_replace_text_at_bkm(combined_sum_doc, "ft_bmk1", ft_text1)
combined_sum_doc <- footers_replace_text_at_bkm(combined_sum_doc, "ft_bmk2", ft_text2)

for (i in 1:length(new_variables)) {
  path <- paste0(getwd(), '/temp_tables/tempsum', i, '.docx')
  combined_sum_doc <- body_add_docx(combined_sum_doc, path, pos = "after") 
}

# Print the combined summary tables document
print(combined_sum_doc, target = paste0(getwd(), '/reports/', survey_year, ' ', site_name, ' Summary Tables.docx')) 
```

**Explanation:**
- **Generate Summary Tables:** The script generates formatted summary tables for each variable in `new_variables`. It utilizes parallel processing to improve performance (`mclapply`). Each table is embedded into a Word document template (`Table_summary_template.docx`), which is then combined into a single report (`Summary Tables.docx`) after inserting headers and footers with appropriate text and metadata.


