---
output: html_document
---

### Cleaning and Mapping Original Variables

```{r, eval = FALSE, echo = TRUE}
data <- raw_data  # Assigning raw_data to data for clarity

# Cleaning and mapping original variables to new standardized variables
eval(parse(text = paste0('data$original_', map_dictionary$site, ' = data$', map_dictionary$standard, sep = '\n')))
```

- **Explanation**:
  - `data <- raw_data`: Copies `raw_data` to `data` for processing.
  - `eval(parse(...))`: Dynamically evaluates expressions to map original variables (`map_dictionary$standard`) to standardized variables (`map_dictionary$site`) within `data`.

### Pre-processing of Secondary Variables

```{r, eval = FALSE, echo = TRUE}
# Reading and processing secondary variables from an Excel sheet
overall_secondary_var_dataset <- read_excel(paste0(getwd(), '/data inputs/mapping_matrix.xlsx'), 'derived_variables') %>%
                                  mutate(
                                    sec_vars = paste0('data$', sec_vars),
                                    req_vars = as.character(list(paste0('data$', eval(parse(text = strsplit(req_vars, ','))))))
                                  ) %>%
                                  rowwise() %>%
                                  mutate(
                                    observ_flag = eval(parse(text = paste0('all(', paste0('!is.null(', eval(parse(text = req_vars)), ')', collapse = ' & '), ')'))),
                                    num_logic = paste0('!is.na(', eval(parse(text = req_vars)), ')', collapse = ' & ')
                                  )

# Filtering secondary dataset for observed variables
secondary_var_dataset <- overall_secondary_var_dataset %>%
                          filter(observ_flag == 'TRUE' & log_cond_denom == 'All')

if (nrow(secondary_var_dataset) > 0) {
  # Applying logic to derive secondary variables
  eval(parse(text = paste0(secondary_var_dataset$sec_vars, ' = NA', sep = '\n')))
  
  # Generating variables based on logic and converting them to factor type
  eval(parse(text = paste0(secondary_var_dataset$sec_vars, '[(', secondary_var_dataset$num_logic, ') & (', secondary_var_dataset$log_cond_num, ')] = 1', sep = '\n')))
  eval(parse(text = paste0(secondary_var_dataset$sec_vars, '[is.na(', secondary_var_dataset$sec_vars, ') & (', secondary_var_dataset$num_logic, ')] = 2', sep = '\n')))
  
  eval(parse(text = paste0(secondary_var_dataset$sec_vars, ' = factor(', secondary_var_dataset$sec_vars, ", levels = 1:2, labels = c('Yes', 'No'))", sep = '\n')))
  
  # Updating mapping matrix with new variables
  eval(parse(text = paste0('updated_matrix$site[updated_matrix$bin_standard == "', sub("data\\$", '', secondary_var_dataset$sec_vars), '"] = "', sub("data\\$", '', secondary_var_dataset$sec_vars), '"', sep = '\n')))
}
```

- **Explanation**:
  - Reads secondary variables from an Excel sheet (`mapping_matrix.xlsx`) and processes them.
  - `overall_secondary_var_dataset`: Includes observed flags and logical conditions for secondary variables.
  - `secondary_var_dataset`: Filters observed secondary variables (`observ_flag == 'TRUE'`) where denominator condition is 'All'.
  - Derives and converts variables (`sec_vars`) based on numeric and logical conditions (`num_logic`).
  - Updates `updated_matrix` with new variables (`site`).

### Handling Derived Variables with Specific Denominators

```{r, eval = FALSE, echo = TRUE}
# Filtering secondary dataset for observed variables with specific denominators
secondary_var_dataset2 <- overall_secondary_var_dataset %>%
                           filter(observ_flag == 'TRUE' & log_cond_denom != 'All')

if (nrow(secondary_var_dataset2) > 0) {
  # Applying logic to derive secondary variables with specific denominators
  eval(parse(text = paste0(secondary_var_dataset2$sec_vars, ' = NA', sep = '\n')))
  
  # Generating variables based on denominator and numerator logic, converting them to factor type
  eval(parse(text = paste0(secondary_var_dataset2$sec_vars, '[(', secondary_var_dataset2$log_cond_denom, ')] = 2', sep = '\n')))
  eval(parse(text = paste0(secondary_var_dataset2$sec_vars, '[(', secondary_var_dataset2$log_cond_denom, ') & (', secondary_var_dataset2$log_cond_num, ')] = 1', sep = '\n')))
  
  eval(parse(text = paste0(secondary_var_dataset2$sec_vars, ' = factor(', secondary_var_dataset2$sec_vars, ", levels = 1:2, labels = c('Yes', 'No'))", sep = '\n')))
  
  # Updating mapping matrix with new variables
  eval(parse(text = paste0('updated_matrix$site[updated_matrix$bin_standard == "', sub("data\\$", '', secondary_var_dataset2$sec_vars), '"] = "', sub("data\\$", '', secondary_var_dataset2$sec_vars), '"', sep = '\n')))
}
```

- **Explanation**:
  - Filters observed secondary variables (`observ_flag == 'TRUE'`) with specific denominators (`log_cond_denom != 'All'`).
  - Derives and converts variables (`sec_vars`) based on denominator and numerator logic (`log_cond_denom`, `log_cond_num`).
  - Updates `updated_matrix` with new variables (`site`).

### Handling Variables with Reduced Denominators

```{r, eval = FALSE, echo = TRUE}
# Identifying variables with reduced denominators and updating data
var_reduced_denom <- updated_matrix %>%
                       filter(!is.na(denominator_resp_reduced))

red_cond_variables <- var_reduced_denom$site

# Iteratively applying logic to set variables to NA based on reduced denominators
for (i in 1:nrow(var_reduced_denom)) {
  red_logical_statements <- paste0(var_reduced_denom$site[i], ' == "', eval(parse(text = paste0(var_reduced_denom$denominator_resp_reduced[i]))), '"', collapse = '|')
}

red_logical_statements <- gsub('q', 'data$q', do.call('c', red_logical_statements))

eval(parse(text = paste0('data$', var_reduced_denom$site, '[', red_logical_statements, '] = NA')))
```

- **Explanation**:
  - `var_reduced_denom`: Identifies variables in `updated_matrix` with reduced denominators (`denominator_resp_reduced`).
  - `red_logical_statements`: Constructs logical statements to set variables to `NA` based on reduced denominators.
  - Applies these statements to update `data` accordingly.

### Generating Summary Matrix for Summary Tables

```{r, eval = FALSE, echo = TRUE}
# Generating a matrix for summary tables
matrix_for_summary_tables <- updated_matrix %>%
                               select(bin_standard, site, numerator, indicator_description) %>%
                               filter(!is.na(numerator))

new_variables <- gsub('\\s|\\t', '', matrix_for_summary_tables[, 1]$bin_standard)  # Binary variables
cond_variables <- matrix_for_summary_tables[, 2]$site  # Site variables
cond_statements <- matrix_for_summary_tables[, 3]$numerator  # Numerators
variable_labels <- matrix_for_summary_tables[, 4]$indicator_description  # Indicator descriptions
```

- **Explanation**:
  - Constructs `matrix_for_summary_tables` from `updated_matrix`, focusing on relevant columns (`bin_standard`, `site`, `numerator`, `indicator_description`).
  - Prepares variables (`new_variables`), site conditions (`cond_variables`), numerator conditions (`cond_statements`), and indicator descriptions (`variable_labels`) for further processing.

### Converting Site Variables to Factor Type and Updating Language Matrix

```{r, eval = FALSE, echo = TRUE}
# Converting site variables (cond_variables) to factor type
eval(parse(text = paste0('data$', unique(cond_variables), '[data$', unique(cond_variables), ' == ""] = NA', sep = '\n ')))
eval(parse(text = paste0('data = data %>% mutate(', paste0(unique(cond_variables), ' = factor(', unique(cond_variables), ')', collapse = ', '), ')')))

# Constructing logical statements based on conditions and applying language labels
logical_statements <- lapply(1:length(new_variables), function(i) {
  if (length(eval(parse(text = paste0(cond_statements[i])))) == 1) {
    paste0(cond_variables[i], ' == ', cond_statements[i])
  } else {
    paste0(cond_variables[i], ' == "', eval(parse(text = paste0(cond_statements[i]))), '"', collapse = '|')
  }
})

logical_statements <- do.call('c', logical_statements)

# Reading language matrix and extracting language titles
language_matrix <- read_excel(paste0(getwd(), '/scripts/LANGUAGES.xlsx')) %>% as.data.frame()
colnames(language_matrix) <- tolower(colnames(language_matrix))
lang_titles <- language_matrix[, tolower(language)]
```

- **Explanation**:
  - Converts empty site variables (`cond_variables`) to `NA` and then to factor type within `data`.
  - Constructs logical statements (`logical_statements`) based on conditions (`cond_statements`).
  - Reads and processes language matrix (`LANGUAGES.xlsx`) for language titles (`lang_titles`).

### Applying Language Titles to New Variables

```{r, eval = FALSE, echo = TRUE}
# Applying language titles to new variables based on logical statements
eval(parse(text = paste0('data = data %>% mutate(', paste0(new_variables, ' = case_when((',
                         logical_statements, ') ~ "', eval(parse(text = lang_titles[1]))[1], '", 
                         !is.na(', cond_variables, ') & !(', logical_statements, ') ~ "',

 eval(parse(text = lang_titles[1]))[2], '"', ')',
                         collapse = ' , '), ')')))
```

- **Explanation**:
  - Applies language titles (`lang_titles`) to new variables (`new_variables`) based on logical conditions (`logical_statements`).

### Writing Weighted Datasets

```{r, eval = FALSE, echo = TRUE}
# Writing two versions of weighted datasets based on compute_BMI_indicators flag
if (compute_BMI_indicators == TRUE) {
  # Version 1 of weighted dataset
  data_v1 <- data
  eval(parse(text = paste0('data_v1$', standard_variables, ' = data_v1$original_', country_variables, sep = '\n')))
  eval(parse(text = paste0('data_v1$', country_variables, ' = data_v1$original_', country_variables, sep = '\n')))
  
  data_v1 <- data_v1 %>% 
    select(-grep('original', names(data_v1), v = T)) %>%
    select(-c(bmiAgeZ, prestrat_wgt, post_adj_factor, post_strat_weights, height, weight, age_cat, grep('q_[0-9]|q[0-9]', names(data_v1), v = T))) %>%
    rename(survey_weight = normalised_weights) %>%
    mutate(record_id = 1:n())
  
  prior_vars <- c('record_id', 'school_id', 'class_id', 'stratum', 'psu', 'survey_weight', 'BMI_status', 'DE_AGE', 'DE_SEX', 'DE_GRADE')
  all_other_variables <- setdiff(names(data_v1), prior_vars)
  combined_vars <- c(prior_vars, all_other_variables)
  
  data_v1 <- data_v1 %>% select(all_of(setdiff(combined_vars, c('school_id', 'class_id', 'category'))))
  data_v1 <- data_v1 %>% rename(weight = survey_weight)
  
  writexl::write_xlsx(data_v1, paste0(getwd(), '/weighted dataset/', gsub('\\(|\\)', '', site_name), ' ', survey_year, ' Weighted Dataset v1.xlsx'))
  
  # Version 2 of weighted dataset
  data_v2 <- data
  eval(parse(text = paste0('data_v2$', standard_variables, ' = data_v2$original_', country_variables, sep = '\n')))
  eval(parse(text = paste0('data_v2$', country_variables, ' = data_v2$original_', country_variables, sep = '\n')))
  
  data_v2 <- data_v2 %>% 
    select(-grep('original', names(data_v2), v = T)) %>%
    select(-c(bmiAgeZ, prestrat_wgt, post_adj_factor, post_strat_weights, height, weight, age_cat, many_similar)) %>%
    rename(survey_weight = normalised_weights) %>%
    mutate(record_id = 1:n())
  
  all_other_variables2 <- setdiff(names(data_v2), prior_vars)
  combined_vars2 <- c(prior_vars, all_other_variables2)
  
  data_v2 <- data_v2 %>% select(all_of(combined_vars2))
  data_v2 <- data_v2 %>% rename(weight = survey_weight)
  
  writexl::write_xlsx(data_v2, paste0(getwd(), '/weighted dataset/', gsub('\\(|\\)', '', site_name), ' ', survey_year, ' Weighted Dataset v2.xlsx'))
  
} else {
  # Version 1 of weighted dataset (no BMI indicators)
  data_v1 <- data
  eval(parse(text = paste0('data_v1$', standard_variables, ' = data_v1$original_', country_variables, sep = '\n')))
  eval(parse(text = paste0('data_v1$', country_variables, ' = data_v1$original_', country_variables, sep = '\n')))
  
  data_v1 <- data_v1 %>% 
    select(-grep('original', names(data_v1), v = T)) %>%
    select(-c(prestrat_wgt, post_adj_factor, post_strat_weights, height, weight, age_cat, many_similar, grep('q_[0-9]|q[0-9]', names(data_v1), v = T))) %>%
    rename(survey_weight = normalised_weights) %>%
    mutate(record_id = 1:n())
  
  prior_vars <- c('record_id', 'school_id', 'class_id', 'stratum', 'psu', 'survey_weight', 'DE_AGE', 'DE_SEX', 'DE_GRADE')
  all_other_variables <- setdiff(names(data_v1), prior_vars)
  combined_vars <- c(prior_vars, all_other_variables)
  
  data_v1 <- data_v1 %>% select(all_of(combined_vars))
  data_v1 <- data_v1 %>% rename(weight = survey_weight)
  
  writexl::write_xlsx(data_v1, paste0(getwd(), '/weighted dataset/', gsub('\\(|\\)', '', site_name), ' ', survey_year, ' Weighted Dataset v1.xlsx'))
  
  # Version 2 of weighted dataset (no BMI indicators)
  data_v2 <- data
  eval(parse(text = paste0('data_v2$', standard_variables, ' = data_v2$original_', country_variables, sep = '\n')))
  eval(parse(text = paste0('data_v2$', country_variables, ' = data_v2$original_', country_variables, sep = '\n')))
  
  data_v2 <- data_v2 %>% 
    select(-grep('original', names(data_v2), v = T)) %>%
    select(-c(prestrat_wgt, post_adj_factor, post_strat_weights, height, weight, age_cat, many_similar)) %>%
    rename(survey_weight = normalised_weights) %>%
    mutate(record_id = 1:n())
  
  all_other_variables2 <- setdiff(names(data_v2), prior_vars)
  combined_vars2 <- c(prior_vars, all_other_variables2)
  
  data_v2 <- data_v2 %>% select(all_of(combined_vars2))
  data_v2 <- data_v2 %>% rename(weight = survey_weight)
  
  writexl::write_xlsx(data_v2, paste0(getwd(), '/weighted dataset/', gsub('\\(|\\)', '', site_name), ' ', survey_year, ' Weighted Dataset v2.xlsx'))
}
```

- **Explanation**:
  - Writes two versions of weighted datasets (`data_v1`, `data_v2`) based on `compute_BMI_indicators` flag.
  - Includes conditions for including or excluding BMI indicators (`bmiAgeZ`, `prestrat_wgt`, etc.) in dataset versions.
  - Writes datasets to Excel files (`xlsx`) named based on site name and survey year.
