---
output: html_document
---

## Survey Design Definition

```{r, eval = FALSE, echo = TRUE}
# Define survey design
svy_data3 <- svydesign(id = ~psu,
                       weights = ~normalised_weights,
                       strata = ~stratum,
                       data = data,
                       nest = TRUE)
```

**Explanation:**
- This section sets up the survey design using the `svydesign` function from the `survey` package. It specifies the sampling design, including primary sampling units (`psu`), weights (`normalised_weights`), strata (`stratum`), and data source (`data`). The `nest = TRUE` parameter indicates that the survey data is nested.

## Function: binary_dictionary

```{r, eval = FALSE, echo = TRUE}
# Function to generate a codebook for binary variables
binary_dictionary <- function(std_var = 'DB_B_HUNGRY', ctry_var = '') {
  
  # Check if the variable is a factor (categorical)
  if (any(class(data[, std_var]) == 'factor')) {
    formula <- make.formula(std_var)
    
    # Calculate frequencies and percentages
    output <- data %>% 
      dplyr::reframe(label_names1 = c("", ""),
                     label_names2 = names(table(data[, std_var])),
                     unweighted_freq = table(eval(parse(text = std_var))),
                     weighted_perc = formatC(round(prop.table(svytable(formula, design = svy_data3)) * 100, 1), format = 'f', digits = 1)
      ) %>% 
      mutate(unweighted_freq = as.character(unweighted_freq),
             weighted_perc = as.character(weighted_perc)) %>%
      dplyr::bind_rows(data %>% 
                        reframe(label_names1 = '',
                                label_names2 = eval(parse(text = lang_titles[2])),
                                unweighted_freq = table(is.na(eval(parse(text = std_var))))['TRUE'],
                                weighted_perc = '')
      ) %>%
      mutate(unweighted_freq = as.character(unweighted_freq),
             weighted_perc = as.character(weighted_perc))
    
    length_output <- nrow(output)
    final_output <- bind_rows(
      c(standard_var = toupper(std_var), country_var = '\t', label_names1 = '\t', label_names2 = '\t', unweighted_freq = '\t', weighted_perc = '\t'),
      c(standard_var = toupper(std_var), country_var = toupper(ctry_var), label_names1 = label(data[, std_var]), label_names2 = '', unweighted_freq = '', weighted_perc = ''),
      bind_cols(standard_var = rep(toupper(std_var), length_output), country_var = rep('', length_output), output)
    )
    
  } else {
    # If the variable is not a factor, handle it differently
    final_output <- bind_rows(
      c(standard_var = toupper(std_var), country_var = '\t', label_names1 = '\t', label_names2 = '\t', unweighted_freq = '\t', weighted_perc = '\t'),
      bind_cols(standard_var = toupper(std_var), country_var = toupper(ctry_var), label_names1 = label(data[, std_var]), label_names2 = '', unweighted_freq = '', weighted_perc = '')
    )
  }
  
  # Set column names and remove row names
  colnames(final_output) <- eval(parse(text = lang_titles[3]))
  rownames(final_output) <- NULL
  
  return(final_output)
}
```

**Explanation:**
- This function, `binary_dictionary`, generates a codebook for a specified binary variable (`std_var`). It checks if the variable is categorical (a factor). If it is, it calculates frequencies and weighted percentages using survey weights (`svy_data3`). If not, it simply retrieves basic information. The function returns a formatted data frame with relevant information.

## Generate Codebook for Binary Variables

```{r, eval = FALSE, echo = TRUE}
# Initialize list to store generated codebooks
generated_binary_dictionary <- list()

# Loop through new_variables to generate codebooks
for (i in 1:length(new_variables)) {
  generated_binary_dictionary[[i]] <- binary_dictionary(std_var = gsub('\t| ', '', new_variables[i]))
}

# Combine codebooks into a single data frame
generated_binary_dictionary <- do.call('rbind', generated_binary_dictionary) %>% as.data.frame()

# Exclude Country Variable Name
generated_binary_dictionary <- generated_binary_dictionary[, -2]

# Identify Cells to Convert to NA
binary_cells_to_NA <- setdiff(as.numeric(gsub('V', '', rownames(generated_binary_dictionary))),
                              as.numeric(rownames(generated_binary_dictionary)[generated_binary_dictionary[, 3] == '']))
```

**Explanation:**
- This section generates codebooks for all specified binary variables (`new_variables`). It uses the `binary_dictionary` function to create individual codebooks, stores them in a list (`generated_binary_dictionary`), and then combines them into a single data frame. It identifies cells that need to be converted to NA based on certain conditions.

## Format for French Language

```{r, eval = FALSE, echo = TRUE}
if (language == 'FRENCH') {
  generated_binary_dictionary[, 5] <- gsub('\\.', ',', generated_binary_dictionary[, 5])
}
```

**Explanation:**
- This snippet checks if the language setting (`language`) is French. If true, it replaces dots with commas in the fifth column (`generated_binary_dictionary[, 5]`), which typically contains percentages formatted for display.

## Generate Flextable

```{r, eval = FALSE, echo = TRUE}
# Generate flextable for the binary dictionary
flex_binary_dictionary <- generated_binary_dictionary %>% 
  flextable() %>%
  flextable::style(pr_t = fp_text(font.family = 'Source Sans Pro'), part = 'all') %>%
  bold(part = 'header') %>%
  hline(i = c(as.numeric(gsub('V', '', rownames(generated_binary_dictionary)[generated_binary_dictionary[, 3] == eval(parse(text = paste0('if (language == "ENGLISH")\n{"Missing"} else if (language == "FRENCH")\n{"Manquant"} else if (language == "SPANISH")\n{"Perdido"} else if (language == "RUSSIAN")\n{"Потерянный"} else {}')))]))), 
        border = fp_border(color = "gray", style = "solid", width = 1)) %>%
  fontsize(size = 9, part = "all") %>%
  autofit() %>%
  merge_h_range(i = c(as.numeric(gsub('V', '', rownames(generated_binary_dictionary)[generated_binary_dictionary[, 3] == '']))), j1 = 2, j2 = 5) %>%
  merge_h_range(i = 1, j1 = 2, j2 = 3, part = 'header') %>%
  width(j = 2, 0.5, unit = "in") %>%
  width(j = 3, 3, unit = "in") %>%
  align(j = 4:5, align = 'right', part = 'all') %>%
  align(j = 2, align = 'center', part = 'header') %>%
  valign(j = 1:5, valign = 'top') %>%
  paginate(group = colnames(generated_binary_dictionary)[1]) %>%
  padding(padding = 0, part = "all") %>%
  compose(j = 1, i = binary_cells_to_NA, value = as_paragraph(as_chunk(NA)))
```

**Explanation:**
- This part generates a formatted table (`flextable`) from `generated_binary_dictionary`. It applies styles, merges cells, adjusts widths, and aligns content for proper display in a Word document. It also handles specific formatting based on the language setting (`language`), such as replacing dots with commas for French.

## Load Template and Replace Content

```{r, eval = FALSE, echo = TRUE}
# Load the Word template
doc <- read_docx("codebook_template.docx")

# Replace placeholders in the template
doc <- headers_replace_text_at_bkm(doc, "country", site_name)
doc <- headers_replace_text_at_bkm(doc, "year", paste0(lang_titles[21], ' ', survey_year))
doc <- headers_replace_text_at_bkm(doc, "Codebook", lang_titles[22])

# Insert flextable into the document
doc <- doc %>% 
  cursor_bookmark(id = "table1") %>%
  body_add_flextable(flex_binary_dictionary, width = dim(flex_binary_dictionary)$widths * 6.5 / (flextable_dim(flex_binary_dictionary)$widths), pos = "on", align = 'left')
```

**Explanation:**
- This section loads a Word document template (`codebook_template.docx`), replaces specific placeholders (`country`, `year`, `Codebook`) with dynamic content (`site_name`, `survey_year`, `lang_titles`), and inserts the generated `flex_binary_dictionary` table into the document at a specified bookmark (`table1`).

## Print the Final Document

```{r, eval = FALSE, echo = TRUE}
# Print the final document to a Word file
print(doc, target = paste0(getwd(), '/reports/', survey_year, ' ', site_name, ' Binary_Codebook.docx'))
```

**Explanation:**
- Finally, this snippet prints the modified Word document (`doc`) to a file (`Binary_Codebook.docx`) in the `reports` directory. The file name includes the survey year (`survey_year`) and site name (`site_name`).
