---
output: html_document
---

### Long School Sample

```{r, eval = FALSE, echo = TRUE}
# Ensure column names are in lowercase
colnames(sample_schools) <- tolower(colnames(sample_schools))

# Adding total enrolment for each school to sample_schools
sample_schools <- sample_schools %>%
  mutate(quantil_grp = case_when(
    enrolment < quantile(enrolment, 0.3333, na.rm = TRUE) ~ 1,
    enrolment >= quantile(enrolment, 0.3333, na.rm = TRUE) &
      enrolment < quantile(enrolment, 0.6666, na.rm = TRUE) ~ 2,
    enrolment >= quantile(enrolment, 0.6666, na.rm = TRUE) ~ 3
  ),
  school_id = as.character(school_id)) 
```

#### Explanation:
- **Column Names Lowercasing**: Ensures all column names in `sample_schools` dataframe are converted to lowercase (`colnames(sample_schools) <- tolower(colnames(sample_schools))`) for consistency.
  
- **Enrolment Quantile Grouping**: Computes a quantile group (`quantil_grp`) for each school based on enrolment numbers using `mutate` and `case_when`. This categorization aids in subsequent statistical analysis.

### Fact Sheet Function

```{r, eval = FALSE, echo = TRUE}
# Fact sheet function definition
fact_sheet_fn <- function(section = factsheet_sections$factsheet_section[1], sub_title = factsheet_sections$sub_title[1]) {
  # Initialize variables
  i <- NULL
  j <- NULL
  all_variable_results <- NULL
  
  # Get variable groups
  var_group <- (factsheet_sections %>% 
                 dplyr::filter(factsheet_section == section))$bin_standard
  
  # Loop through each variable group
  for (i in var_group) {
    outputs <- c()
    # Loop through each condition
    for (j in log_conditions) {
      # Construct formula dynamically
      num_var <- eval(parse(text = lang_titles[1]))[1]
      formula <- make.formula(paste0(i, '=="', num_var, '"'))
      
      # Calculate proportion and confidence interval using survey functions
      est_ciprop <- svyciprop(formula, design = subset(svy_data3, eval(parse(text = j))), method = "lo", df = degrees_freedom)
      est_ci <- paste0(
        formatC(round(as.vector(est_ciprop) * 100, 1), format = 'f', digits = 1), '\n(',
        formatC(round((as.numeric(attr(est_ciprop, "ci")[1])) * 100, 1), format = 'f', digits = 1), ' - ',
        formatC(round(100 * as.numeric(attr(est_ciprop, "ci")[2]), 1), format = 'f', digits = 1), ')'
      )
      
      # Adjust output based on participant count
      n_participants <- data %>% 
        filter(eval(parse(text = paste0('!is.na(', i, ') & (', j, ')')))) %>% 
        reframe(n()) %>% 
        as.numeric()
      est_ci <- ifelse(n_participants >= 100, est_ci, '-') # Show '-' if participant count is less than 100
      
      outputs <- c(outputs, est_ci)
    }
    var_output <- c(label(data[, i]), outputs) # Construct output row with variable label and results
    all_variable_results <- rbind(all_variable_results, var_output) # Append to results dataframe
    rownames(all_variable_results) <- NULL # Reset row names for cleanliness
  }
  
  # Add subtitle row and return final formatted results
  final_var_results <- rbind(c(sub_title, rep('', 3)), all_variable_results)
  return(final_var_results)
}
```

#### Explanation:
- **Function Definition**: Defines `fact_sheet_fn`, which generates a fact sheet based on given `section` and `sub_title`. It dynamically calculates proportions and confidence intervals using survey data (`svy_data3`), iterating through variable groups (`var_group`) and conditions (`log_conditions`).
  
- **Variable Group Loop**: Iterates over each variable group (`var_group`). For each group:
  - **Condition Loop**: Iterates through each condition (`log_conditions`). Constructs formulas dynamically and computes statistics (`svyciprop`).
  
- **Participant Adjustment**: Adjusts output (`est_ci`) based on participant count (`n_participants`). Shows `'-'` if participant count is less than 100.

### Generating Fact Sheet

```{r, eval = FALSE, echo = TRUE}
# Generate fact sheets for each section
i <- NULL
full_fact_sheet <- NULL
for (i in sort(unique(factsheet_sections$factsheet_section))) {
  corresp_subtitle <- unique(factsheet_sections$sub_title[factsheet_sections$factsheet_section == i])
  fact_subtable <- fact_sheet_fn(section = i, sub_title = corresp_subtitle)
  full_fact_sheet <- rbind(full_fact_sheet, fact_subtable)
}
```

#### Explanation:
- **Fact Sheet Generation Loop**: Iterates through unique sections (`factsheet_sections$factsheet_section`). For each section:
  - Retrieves corresponding subtitle (`corresp_subtitle`) and calls `fact_sheet_fn` to generate a fact table (`fact_subtable`).
  - Appends each generated fact table to `full_fact_sheet` for comprehensive reporting.

### Document Preparation and Output

```{r, eval = FALSE, echo = TRUE}
# Prepare fact sheet for output
rev_full_fact_sheet <- full_fact_sheet %>% as.data.frame()

# Adjust column names based on language
if (language == 'FRENCH') {
  rev_full_fact_sheet <- eval(parse(text = paste0('cbind(', paste0(gsub('\\.', ',', rev_full_fact_sheet), collapse = ','), ')'))) %>% as.data.frame()
} else {
  colnames(rev_full_fact_sheet) <- eval(parse(text = lang_titles[19]))
}

# Create a flextable for the fact sheet
flex_fact_sheet <- rev_full_fact_sheet %>% 
  flextable() %>% 
  autofit() %>%
  flextable::style(pr_t = fp_text(font.size = 10, font.family = 'Source Sans Pro'), part = 'all') %>%
  bold(i = subtitle_nrows) %>%
  bg(bg = "white", i = 1, part = "header") %>%
  theme_box() %>%
  align(align = "center", j = 2:4, part = "all") %>%
  merge_h_range(i = subtitle_nrows, j1 = 1, j2 = 4) %>%
  width(j = 2:4, 4.3, unit = "in") %>%
  bg(bg = "#C9DDF3", i = 1, part = "header") %>%
  bg(bg = "#009ADE", i = subtitle_nrows, part = "body") %>%
  padding(padding = 0, part = "all") %>%
  paginate()

# Generate Factsheet
if (is_this_census == FALSE) {
  doc <- read_docx(paste0(getwd(), '/templates/fact_sheet_template_', language, '.docx'))
} else {
  doc <- read_docx(paste0(getwd(), '/templates/census_fact_sheet_template_', language, '.docx'))
}

# Replace placeholders in document
doc <- headers_replace_text_at_bkm(doc, "country", site_name)
doc <- headers_replace_text_at_bkm(doc, "year", paste0(lang_titles[29], ' ', survey_year))
doc <- headers_replace_text_at_bkm(doc, "Fact", lang_titles[26])

# Add additional text based on survey type
if (is_this_census == FALSE) {
  additional_text <- c(
    paste0(survey_year, ' ', site_name),
    paste0(levels(data$DE_GRADE)[1], ' - ', levels(data$DE_GRADE)[length(levels(data$DE_GRADE))]),
    paste0(levels(data$DE_GRADE)[1], ' - ', levels(data$DE_GRADE)[length(levels(data$DE_GRADE))]),
    site_name,
    sum(sample_schools$school_part == 1 | sample_schools$school_part == 0, na.rm = TRUE),
    site_name,
    paste0(paste0(sort(unique(factsheet_sections$sub_title))[-length(unique(factsheet_sections$sub_title))], collapse = '; '),
           '; & ', sort(unique(factsheet_sections$sub_title))[length(unique(factsheet_sections$sub_title))]),
    paste0(formatC(round(100 * (sum(sample_schools$school_part == 1, na.rm = TRUE) / sum(sample_schools$school_part == 1 | sample_schools$school_part == 0, na.rm = TRUE)), 1), format = 'f', digits = 1), '%'),
    paste0(formatC(round(100 * (sum(long_school_sample$stpart, na.rm = TRUE) / sum(long_school_sample$cenrol, na.rm = TRUE)), 1), format = 'f', digits = 1), '%'),
    paste0(formatC(round(100 * (sum(sample_schools$school_part == 1, na.rm = TRUE) / sum(sample_schools$school_part == 1 | sample_schools$school_part == 0, na.rm = TRUE)) * (sum(long_school_sample$stpart, na.rm = TRUE) / sum(long_school_sample$cenrol, na.rm = TRUE)), 1), format = 'f', digits = 1), '%'),
    nrow(data),
    site_name


  )
  
  bmks <- paste0('bmk', 1:length(additional_text))
  eval(parse(text = paste0('doc <- body_replace_text_at_bkm(doc, "', bmks, '", "', additional_text, '")')))
} else {
  additional_text <- c(
    paste0(survey_year, ' ', site_name),
    paste0(levels(data$DE_GRADE)[1], ' - ', levels(data$DE_GRADE)[length(levels(data$DE_GRADE))]),
    paste0(levels(data$DE_GRADE)[1], ' - ', levels(data$DE_GRADE)[length(levels(data$DE_GRADE))]),
    site_name,
    site_name,
    paste0(paste0(sort(unique(factsheet_sections$sub_title))[-length(unique(factsheet_sections$sub_title))], collapse = '; '),
           '; & ', sort(unique(factsheet_sections$sub_title))[length(unique(factsheet_sections$sub_title))]),
    paste0(formatC(round(100 * (sum(sample_schools$school_part == 1, na.rm = TRUE) / sum(sample_schools$school_part == 1 | sample_schools$school_part == 0, na.rm = TRUE)), 1), format = 'f', digits = 1), '%'),
    paste0(formatC(round(100 * (sum(long_school_sample$stpart, na.rm = TRUE) / sum(long_school_sample$cenrol, na.rm = TRUE)), 1), format = 'f', digits = 1), '%'),
    paste0(formatC(round(100 * (sum(sample_schools$school_part == 1, na.rm = TRUE) / sum(sample_schools$school_part == 1 | sample_schools$school_part == 0, na.rm = TRUE)) * (sum(long_school_sample$stpart, na.rm = TRUE) / sum(long_school_sample$cenrol, na.rm = TRUE)), 1), format = 'f', digits = 1), '%'),
    nrow(data),
    site_name
  )
  
  bmks <- paste0('bmk', 1:length(additional_text))
  eval(parse(text = paste0('doc <- body_replace_text_at_bkm(doc, "', bmks, '", "', additional_text, '")')))
}

# Add flextable to document
doc <- doc %>% cursor_bookmark(id = "table1") %>%
  body_add_flextable(
    width(flex_fact_sheet, width = dim(flex_fact_sheet)$widths * 7.25 / (flextable_dim(flex_fact_sheet)$widths)),
    pos = "on", align = 'left'
  )

# Save the document
print(doc, target = paste0(getwd(), '/reports/', survey_year, ' ', site_name, ' Factsheet.docx'))
```

### Explanation:
- **Document Preparation**: Reads a template document (`fact_sheet_template_*.docx` or `census_fact_sheet_template_*.docx`) based on the language (`language`). This template likely contains placeholders for site name, year, and other details.
  
- **Text Replacement**: Replaces placeholders (`country`, `year`, `Fact`) in the document with actual survey details (`site_name`, `survey_year`, `lang_titles`).
  
- **Additional Text**: Depending on whether it's a census or not (`is_this_census`), prepares additional text (`additional_text`) for insertion into the document. This text includes survey details, counts, percentages, etc.
  
- **Flextable Integration**: Inserts a flextable (`flex_fact_sheet`) into the document at bookmark `table1`, ensuring proper formatting and alignment.
  
- **Document Output**: Finally, saves the updated document as `survey_year site_name Factsheet.docx` in the `/reports/` directory.
